\vspace{1.0cm} \LARGE \bf The ability of single genes vs full genomes to resolve time and space in outbreak analysis

### 2019-03-19 genomic-horizon.tex
Add title and fix text size
Fix S figure, add title.
Change email address.
Fix probability-weighted distance for S figure.

%%% TITLE %%%
\title{\vspace{1.0cm} \LARGE \bf Genomic horizon}

@@

\affil[1]{Vaccine and Infectious Disease Division, Fred Hutchinson Cancer Research Center, Seattle, WA, USA}
\affil[2]{Gothenburg Global Biodiversity Center, Gothenburg, Sweden}
\begin{document}

@@

$\ast$ \footnotesize{Corresponding author (gdudas@fredhutch.org)}

@@

\begin{figure}[h]
 \centering
	\includegraphics[width=0.75\textwidth]{supp_figures/sfigX_treetimeLocations.png}
	\caption{\textbf{Maximum likelihood inference of masked sequence location from genomes (left) and GP sequences (right) via a CTMC model implemented in TreeTime.}
  Unlike the Bayesian GLM where probabilities are spread across different locations, the CTMC gives categorical support to one location.
  Genomes still perform better in terms of correct guess (0.432 probability that best guess location is true location for genomes versus 0.259 for GP), cross entropy (12012.800 nats for genome versus 24397.109 nats for GP) and mean probability-weighted great circle distance between true location population centroid and estimated location population centroid (2.304 km for genome versus 3.287 km for GP).
	}
	\label{TTlocations}
\end{figure}

>>>>

%%% TITLE %%%
\title{\vspace{1.0cm} \LARGE \bf The ability of single genes vs full genomes to resolve time and space in outbreak analysis}

@@

\affil[1]{Vaccine and Infectious Disease Division, Fred Hutchinson Cancer Research Center, Seattle, WA, USA}
\affil[2]{Gothenburg Global Biodiversity Center, Gothenburg, Sweden}
\affil[$\ast$]{Corresponding author (gytisdudas@gmail.com)}
\begin{document}

@@

@@

\begin{figure}[h]
 \centering
	\includegraphics[width=0.75\textwidth]{supp_figures/sfigX_treetimeLocations.png}
	\caption{\textbf{Maximum likelihood inference of masked sequence location from genomes (left) and GP sequences (right) via a CTMC model implemented in TreeTime.}
  Unlike the Bayesian GLM where probabilities are spread across different locations, the CTMC gives categorical support to one location.
  Genomes still perform better in terms of correct guess (0.432 probability that best guess location is true location for genomes versus 0.259 for GP), cross entropy (12012.800 nats for genome versus 24397.109 nats for GP) and mean probability-weighted great circle distance between true location population centroid and estimated location population centroid (87.568 km for genome versus 124.909 km for GP).
	}
	\label{TTlocations}
\end{figure}
